---
title: "HW7"
author: "Rachael Valdez"
date: "10/10/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data Import
We begin by importing the data from the california-state-university-2015.csv file and using as.character to test for object of type "character".

```{r dataimport}
df = read.csv("../data/california-state-university-2015.csv")
df$Employee.Name = as.character(df$Employee.Name)
```

## Employees with the name Martinez

```{r EmployeeMartinez}
my_pattern = "Martinez"
NameMartinez = df$Employee.Name[grepl(my_pattern, df$Employee.Name)]
print(NameMartinez)
```

## Employees whose name starts with the letters "Wil"

```{r BeginningWil}
my_pattern = "^Wil"
BegWil = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(BegWil)
```

## Employees with hyphenated name

```{r hyphen}
my_pattern = "-"
hyp = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(hyp)
```

## Middle Name "Paul"

```{r middle}
my_pattern = "[A-Z][a-z]{1,} Paul [A-Z][a-z]{1,}"
middle = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(middle)
```

## Last Name Martinez

```{r last}
my_pattern = "[A-Z][a-z]{1,} [A-Z][a-z]{1,} Martinez"
Last = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(Last)
```

## Last Name Martinez, no hyphens

```{r lastNoHyphen}
#my_pattern = "[A-Z][a-z]{1,} [A-Z][a-z]{1,} Martinez$"
my_pattern = "[A-Z][a-z]{1,} Martinez$"
LastNH = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(LastNH)
```

## First name starts with "E", has a middle initial, and last name is 'Martinez'

```{r EmiddleMartinez}
my_pattern = "E[a-z]{1,} [A-Z] Martinez"
ExMartinez = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(ExMartinez)
```
## First name starts with "E", has no middle initial, and last name is 'Martinez'

```{r EnomiddleMartinez}
#my_pattern = "[E][a-z]{1,} Martinez"
my_pattern = "[E][a-z]{1,} Martinez"
ExMartinez = df$Employee.Name[grepl((my_pattern), df$Employee.Name)]
print(ExMartinez)
```
