---
title: "HW8 RV"
author: "Rachael Valdez"
date: "10/24/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Importing Files
12 .csv files will be imported and bound together to create one large file using a loop.
These files contain information regaurding the time and temperature per trial number conducted. 
```{r importingFiles} 
fnames = dir("../data/temperature_trials", full.names=TRUE)

for (i in 1: length(fnames) ) {
  #open each file in turn
  temp = read.csv(fnames[i])
  temp$DateTime = as.POSIXct(temp$DateTime, origin = '1970-1-1', tz="")
  temp$elapsedTime = difftime(temp$DateTime, temp$DateTime[1], units='mins')
  temp$elapsedTimeMin = as.numeric(temp$elapsedTime)
  
  #pull out file name trial number
  loc = regexpr(pattern = "Trial[0-9]*", text = fnames[i])

  trialNumber = as.numeric(substr(fnames[i], start = loc[[1]][1]+5,
          stop = loc[[1]][1] + attr(loc, 'match.length')-1))
  #print(trialNumber)
  temp$trialNumber = as.numeric(trialNumber)
  
  if (i == 1) {
    res = temp
  } else {
      res = rbind(res, temp)
    }
}


res$POSIXt = as.POSIXct(res$POSIXt, origin = '1970-1-1', tx="")

```

#Plot 1
Data frame will be plotted to get the temperature for each TC0 time point.
```{r plotRes}

plot(x = res$elapsedTimeMin[res$trialNumber==1], y = res$TC0[res$trialNumber==1], type = 'l',
       #main = "Channel TC0 for each Trial",
       ylab = 'Temperature, C',
       xlab = 'Elapsed Time, minutes',
     las = 1,#turns y axis 
     xlim = c(0, max(res$elapsedTimeMin)),
     ylim = c(min(res$TC0), max(res$TC0)))
mtext(text = "Channel TC0 for each Trial", side = 3, line = 1, cex = 1.5,
      adj = 0)
     #xlim = c(0, 150),
     #ylim = c(15,35)) 

trialNums = unique(res$trialNumber)  
for(y in 2:length(trialNums)) {
      lines(x = res$elapsedTimeMin[res$trialNumber==trialNums[y]], y = res$TC0[res$trialNumber==trialNums[y]], col = y)
}


```

## Importing excel 
Heating trial info will be imported which contains mussel tag ID's,the channel, trial number information, and if the specimin is dead or alive. 
```{r importHTinfo}
#Extract xlsx for plot 2 

library(readxl)
heatingInfo = read_xlsx("../data/Heating_trial_info.xlsx")
heatingInfo$TrialNumber = as.character(heatingInfo$TCchannel)
```

##Plot 2
Plot two will parce out TCLocation for In50 for each trial 1-12.

```{r pl, echo=FALSE}

trial1 = read.csv(fnames[1])
TrialNumber = 1
T1 = cbind(TrialNumber, trial1)  #add column
T1$POSIXt = ((T1$POSIXt-1500032605)/60)

trial2 = read.csv(fnames[2])
TrialNumber = 2
T2 = cbind(TrialNumber, trial2)  #add column
T2$POSIXt = ((T2$POSIXt-1500036845)/60)

trial3 = read.csv(fnames[3])
TrialNumber = 3
T3 = cbind(TrialNumber, trial3)  #add column
T3$POSIXt = ((T3$POSIXt-1500041435)/60)

trial4 = read.csv(fnames[4])
TrialNumber = 4
T4 = cbind(TrialNumber, trial4)  #add column
T4$POSIXt = ((T4$POSIXt-1500571915)/60)

trial5 = read.csv(fnames[5])
TrialNumber = 5
T5 = cbind(TrialNumber, trial5)  #add column
T5$POSIXt = ((T5$POSIXt-1500628845)/60)

trial6 = read.csv(fnames[6])
TrialNumber = 6
T6 = cbind(TrialNumber, trial6)  #add column
T6$POSIXt = ((T6$POSIXt-1500641795)/60)

trial7 = read.csv(fnames[7])
TrialNumber = 7
T7 = cbind(TrialNumber, trial7)  #add column
T7$POSIXt = ((T7$POSIXt-1500649485)/60)

trial8 = read.csv(fnames[8])
TrialNumber = 8
T8 = cbind(TrialNumber, trial8)  #add column
T8$POSIXt = ((T8$POSIXt-1500805875)/60)

trial9 = read.csv(fnames[9])
TrialNumber = 9
T9 = cbind(TrialNumber, trial9)  #add column
T9$POSIXt = ((T9$POSIXt-1500885615)/60)

trial10 = read.csv(fnames[10])
TrialNumber = 10
T10 = cbind(TrialNumber, trial10)  #add column
T10$POSIXt = ((T10$POSIXt-1501580645)/60)

trial11 = read.csv(fnames[11])
TrialNumber = 11
T11 = cbind(TrialNumber, trial11)  #add column
T11$POSIXt = ((T11$POSIXt-1501580645)/60)

trial12 = read.csv(fnames[12])
TrialNumber = 12
T12 = cbind(TrialNumber, trial12)  #add column
T12$POSIXt = ((T12$POSIXt-1501603975)/60)

res = rbind(T1, T2, T3, T4, T5, T6, T7, T8, T9, T10, T11, T12)

res$DateTime = as.POSIXct(res$DateTime, origin = '1970-1-1', tz="")


One = T1[,c(1:2,4)]
  colnames(One)[colnames(One) == 'TC0'] <- 'In50'
Two = T2[,c(1:2,7)]
  colnames(Two)[colnames(Two) == 'TC3'] <- 'In50'
Three = T3[,c(1:2,7)]
  colnames(Three)[colnames(Three) == 'TC3'] <- 'In50'
Four = T4[,c(1:2,7)]
  colnames(Four)[colnames(Four) == 'TC3'] <- 'In50'  
Five = T5[,c(1:2,4)]
  colnames(Five)[colnames(Five) == 'TC0'] <- 'In50'  
Six = T6[,c(1:2,4)]
  colnames(Six)[colnames(Six) == 'TC0'] <- 'In50'  
Seven = T7[,c(1:2,6)]
  colnames(Seven)[colnames(Seven) == 'TC2'] <- 'In50'  
Eight = T8[,c(1:2,8)]
  colnames(Eight)[colnames(Eight) == 'TC4'] <- 'In50'  
Nine = T9[,c(1:2,8)]
  colnames(Nine)[colnames(Nine) == 'TC4'] <- 'In50' 
Ten = T10[,c(1:2,7)]
  colnames(Ten)[colnames(Ten) == 'TC3'] <- 'In50' 
Eleven = T11[,c(1:2,8)]
  colnames(Eleven)[colnames(Eleven) == 'TC4'] <- 'In50'  
Twelve = T12[,c(1:2,7)]
  colnames(Twelve)[colnames(Twelve) == 'TC3'] <- 'In50'
  
  Bind = rbind(One, Two, Three, Four, Five, Six, Seven, Eight, Nine, Ten, Eleven, Twelve)


```

```{r plot1, echo=FALSE}

plot(x = Bind$POSIXt, y = Bind$In50, type = 'l',
       main = "Channel TC0 for each Trial",
       ylab = 'Temperature, C',
       xlab = 'Elapsed Time, minutes',
     ylim = c(15,35)) 

```


