---
title: "HW 9"
author: "Rachael Valdez"
date: "10/31/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Data Import
Data file, .txt, will be imported. The Columns will be named and the max of each column will be calculated. 

```{r dataImport}
fname = ("../data/Portfoliofiles/2017-1010Plate 1 TM032.txt")
df = read.table(file = fname, header = FALSE, sep = "\t", skip = 4, fileEncoding = "", check.names = FALSE, nrows = 50)

colNames = c('Time', 'TemperatureC')
colLetters = LETTERS[1:8]
for(i in 1:length(colLetters)) {
  for(j in 1:12) {
    temp = paste(colLetters[i], j, sep = "")
    colNames = c(colNames, temp)
    }
}
colnames(df) = colNames
apply(df, 2, function(df) maxx, na.rm = TRUE)

Max = apply(df,2,max)
df1 = rbind(df, Max) #add max of each column to last row
myData = df1[-c(1:50), -c(1,2) ] #gathered headers and max values

#install.packages('reshape2')
library(reshape2)
mydt = dcast(myData,X~Y,value.var = "Z")
```

##Strain analysis
Each bacterial strain will have the average, standard deviation and CV calculated and output onto a table for each sample.

##Strain specification
A list for each strain showing a pass or fail based on the set specifications will be output with the result for the ontest.

##% Recovery Graph
A graph showing the distribution of % recovery for each strain and sample will be plotted.
The percent recovery will be caluclated and output for each strain and sample.

##Box Plot
A boxplot showing the distribution for each stain will be plotted.









