---
title: "TM032"
author: "Rachael Valdez"
date: "November 10, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Java}
if (Sys.getenv("JAVA_HOME")!="")
  Sys.setenv(JAVA_HOME="")
```
###Test Method
This test method analysis will be used to determine if fast protein liquid chromatography(FPLC) and tangential flow filtration(TFF) meet the set specifications for each run to be built into production.Several samples throughout the downstream processing will be tested to make sure the protein is still functional and loss during processing is minimized. The protein is tested for activity at 8% against 4 positive and 1 negative bacterial strains to make sure the protein is targeting set organisms. Using a Spectramax-L, luminescence is measured over 12.5 seconds. The data generated is from a Spectramax-L which outputs a .txt file which will be imported. 

###Data Analysis
1: Import data and libraries

2: Calculated averages

3: Calculated standard deviation

4: Calculated CV

5: Generate strain analysis chart with pass or fail

6: Generate dot plot

7: Generate bar graph

8: Data export

  Note: Before running script go to section 8 and input a unique name identifier so files do not save over each other.


### 1: Data Import
Data file, .txt, will be imported. The columns will be named and the peak of each well will be calculated. 

```{r Data}
##Set your directory to folder with your data

spec <- file.choose()
data = read.table(spec, header=FALSE, sep='\t', skip = 3,nrows = 50)
colNames = c('Time', 'TemperatureC')
colLetters = LETTERS[1:8]
for(i in 1:length(colLetters)) {
  for(j in 1:12) {
    temp = paste(colLetters[i], j, sep = "")
    colNames = c(colNames, temp)
    }
}
colnames(data) = colNames

Max = apply(data,2,max)
#print(Max)
df = rbind(data, Max) #add max of each column to last row
myData = round(df[-c(1:50), -c(1,2) ]) #gathered headers and max values
MaxValues = t(myData) #Transpose data frame
colnames(MaxValues)[1] <- "Max_RLU" #name column
PeakValues = data.frame(na.omit(MaxValues)) #remove values with NA


###Libraries
library(xlsx)
library(rJava)
library(xlsxjars)
library(ggplot2)
library(reshape2)

```

###Strain Analysis
Each bacterial strain tested will have the average, standard deviation and CV calculated. Based off of these calulations a chart will be output with the set specifications and a pass or fail output.

### 2: Peak Value
```{r Mean}
###AVC Means
Strain1 <- rowMeans(myData[,1:2])
Strain2 <- rowMeans(myData[,3:4])
Strain3 <- rowMeans(myData[,5:6])
Strain4 <- rowMeans(myData[,7:8])
Strain5 <- (myData[,9])
Strain6 <- (myData[,10])
AVCMean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(AVCMean)[1] <- "AVC" #name column
AVCMean = t(AVCMean)

###Retentate Means
Strain1 <- rowMeans(myData[,13:14])
Strain2 <- rowMeans(myData[,15:16])
Strain3 <- rowMeans(myData[,17:18])
Strain4 <- rowMeans(myData[,19:20])
Strain5 <- (myData[,21])
Strain6 <- (myData[,22])
RetMean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(RetMean)[1] <- "Retentate" #name column
RetMean = t(RetMean)

###Eluate Means
Strain1 <- rowMeans(myData[,25:26])
Strain2 <- rowMeans(myData[,27:28])
Strain3 <- rowMeans(myData[,29:30])
Strain4 <- rowMeans(myData[,31:32])
Strain5 <- (myData[,33])
Strain6 <- (myData[,34])
EluMean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(EluMean)[1] <- "Eluate" #name column
EluMean = t(EluMean)

###Lys Means
Strain1 <- rowMeans(myData[,37:38])
Strain2 <- rowMeans(myData[,39:40])
Strain3 <- rowMeans(myData[,41:42])
Strain4 <- rowMeans(myData[,43:44])
Strain5 <- (myData[,45])
Strain6 <- (myData[,46])
LysMean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(LysMean)[1] <- "Lysate" #name column
LysMean = t(LysMean)

###LM Means
Strain1 <- rowMeans(myData[,49:50])
Strain2 <- rowMeans(myData[,51:52])
Strain3 <- rowMeans(myData[,53:54])
Strain4 <- rowMeans(myData[,55:56])
Strain5 <- (myData[,57])
Strain6 <- (myData[,58])
LMMean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(LMMean)[1] <- "LM" #name column
LMMean = t(LMMean)

###FT Means
Strain1 <- rowMeans(myData[,61:62])
Strain2 <- rowMeans(myData[,63:64])
Strain3 <- rowMeans(myData[,65:66])
Strain4 <- rowMeans(myData[,67:68])
Strain5 <- (myData[,69])
Strain6 <- (myData[,70])
FTMean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(FTMean)[1] <- "FT" #name column
FTMean = t(FTMean)

###Wash1 Means
Strain1 <- rowMeans(myData[,73:74])
Strain2 <- rowMeans(myData[,75:76])
Strain3 <- rowMeans(myData[,77:78])
Strain4 <- rowMeans(myData[,79:80])
Strain5 <- (myData[,81])
Strain6 <- (myData[,82])
W1Mean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(W1Mean)[1] <- "Wash1" #name column
W1Mean = t(W1Mean)

###Wash2 Means
Strain1 <- rowMeans(myData[,85:86])
Strain2 <- rowMeans(myData[,87:88])
Strain3 <- rowMeans(myData[,89:90])
Strain4 <- rowMeans(myData[,91:92])
Strain5 <- (myData[,93])
Strain6 <- (myData[,94])
W2Mean = rbind(Strain1, Strain2, Strain3, Strain4, Strain5, Strain6)
colnames(W2Mean)[1] <- "Wash2" #name column
W2Mean = t(W2Mean)

Mean = rbind(AVCMean, RetMean, EluMean, LysMean, LMMean, FTMean, W1Mean, W2Mean)
Mean = as.data.frame(round(Mean))
print(Mean)

```

### 3: Standard Deviation
```{r StDev}
###AVC SD
Strain1 <- sd(myData[,1:2])
Strain2 <- sd(myData[,3:4])
Strain3 <- sd(myData[,5:6])
Strain4 <- sd(myData[,7:8])
AVCSD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(AVCSD)[1] <- "AVC" #name column
AVCSD = t(AVCSD)

###Retentate SD
Strain1 <- sd(myData[,13:14])
Strain2 <- sd(myData[,15:16])
Strain3 <- sd(myData[,17:18])
Strain4 <- sd(myData[,19:20])
RetSD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(RetSD)[1] <- "Retentate" #name column
RetSD = t(RetSD)

###Eluate SD
Strain1 <- sd(myData[,25:26])
Strain2 <- sd(myData[,27:28])
Strain3 <- sd(myData[,29:30])
Strain4 <- sd(myData[,31:32])
EluSD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(EluSD)[1] <- "Eluate" #name column
EluSD = t(EluSD)

###Lys SD
Strain1 <- sd(myData[,37:38])
Strain2 <- sd(myData[,39:40])
Strain3 <- sd(myData[,41:42])
Strain4 <- sd(myData[,43:44])
LysSD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(LysSD)[1] <- "Lysate" #name column
LysSD = t(LysSD)

###LM SD
Strain1 <- sd(myData[,49:50])
Strain2 <- sd(myData[,51:52])
Strain3 <- sd(myData[,53:54])
Strain4 <- sd(myData[,55:56])
LMSD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(LMSD)[1] <- "LM" #name column
LMSD = t(LMSD)

###FT SD
Strain1 <- sd(myData[,61:62])
Strain2 <- sd(myData[,63:64])
Strain3 <- sd(myData[,65:66])
Strain4 <- sd(myData[,67:68])
FTSD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(FTSD)[1] <- "FT" #name column
FTSD = t(FTSD)

###Wash1 SD
Strain1 <- sd(myData[,73:74])
Strain2 <- sd(myData[,75:76])
Strain3 <- sd(myData[,77:78])
Strain4 <- sd(myData[,79:80])
W1SD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(W1SD)[1] <- "Wash1" #name column
W1SD = t(W1SD)

###Wash2 SD
Strain1 <- sd(myData[,85:86])
Strain2 <- sd(myData[,87:88])
Strain3 <- sd(myData[,89:90])
Strain4 <- sd(myData[,91:92])
W2SD = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(W2SD)[1] <- "Wash2" #name column
W2SD = t(W2SD)

SD = rbind(AVCSD, RetSD, EluSD, LysSD, LMSD, FTSD, W1SD, W2SD)
SD = as.data.frame(round(SD))

print(SD)

```

### 4: Coefficient of Variation
```{r CV }

CV = ((SD/Mean[,1:4])*100)
CV = round(CV,2)
print(CV)

```

### 5: Strain Specification
Each positive control will have a pass or fail based on set specification output.
If one strain does not pass, the test method failed.
```{r Signal}

TMsignal = log(Mean[2,])/log(Mean[4,])

TMsignal1 = TMsignal[,1:4]

Strain1 = ifelse(TMsignal$Strain1 > 0.9 & TMsignal$Strain1 < 1.25, "Pass", "Fail")
Strain2 = ifelse(TMsignal$Strain2 > 0.95 & TMsignal$Strain2 < 1.25, "Pass", "Fail")
Strain3 = ifelse(TMsignal$Strain3 > 0.95 & TMsignal$Strain3 < 1.5, "Pass", "Fail")
Strain4 = ifelse(TMsignal$Strain4 > 0.95 & TMsignal$Strain4 < 1.5, "Pass", "Fail")

TMResult = rbind(Strain1, Strain2, Strain3, Strain4)
TMResult = t(TMResult)
TMResults = rbind(TMsignal1, TMResult)
TMResults = t(TMResults)
colnames(TMResults)[2] <- "TMSpec" 
TMResults = as.data.frame(TMResults)
print(TMResults)

```

### 6:Dot plot
Plot showing RLU distribution for each strain
```{r ggplot }
## Looking at 4 positive strains

M1 = Mean[1:4,1:4]
df <- melt(M1)

df$rowid <- c('AVC', 'Retentate', 'Eluate', 'Lysate')
P <- ggplot(df, aes(x = factor(variable), y = value)) + geom_jitter(width = 0.1, height = 0, 
                                                           aes(color=factor(rowid))) + xlab("Strains") + ylab("RLU") + ggtitle("RLU Distribution") + theme(plot.title = element_text(hjust = 0.5)) +
  labs(color='Samples') 

print(P)


```


### 7: % Recovery graph
Graph showing distribution of % recovery for each strain and sample calculation output for each sample.

```{r bargraph, fig.width=8, fig.height=5}

#Elution Volumes
EluVol = 0.045
LysVol = 0.1
LMVol = 0.2
FTVol = 0.2
W1Vol = 0.045
W2Vol = 0.09

# % Recovery Calculations 
M2 = Mean[3:8,1:4]
L1 = M2[2,]*LysVol
Lys = M2[2,]*LysVol/L1
LM = M2[3,]*LMVol/L1
FT = M2[4,]*FTVol/L1
Wash1 = M2[5,]*W1Vol/L1
Wash2 = M2[6,]*W2Vol/L1
Eluate = M2[1,]*EluVol/L1

R1 = rbind(Lys, LM, FT, Wash1, Wash2, Eluate)
R1 = round(R1,2)
R1 = R1*100
R1 = round(R1, 0)

Recovery = R1[-1,]
Recovery = Recovery[-1,]

Strain1 = sum(Recovery[1:4, 1])
Strain2 = sum(Recovery[1:4, 2])
Strain3 = sum(Recovery[1:4, 3])
Strain4 = sum(Recovery[1:4, 4])

Recovery1 = rbind(Strain1, Strain2, Strain3, Strain4)
colnames(Recovery1)[1] <- "Sum"
Recovery1 = t(Recovery1)

Recovery2 = rbind(Recovery, Recovery1)
print(Recovery2)

Recovery = as.matrix(Recovery)

##Barplot
barplot(Recovery, main = "% Recovery", 
        xlab = "",
        ylab = "Percentage",
        legend.text = TRUE,
        col = c("Orange", "Green", "Forestgreen", "Blue"))


```

### 8: Data Export
Create a unique name identifier for saving files each time script is run. 
Example:"../Data/Plate1_PeakValues.xlsx"

```{r exports, echo = TRUE}

write.xlsx(PeakValues, "../data/Plate2_PeakValues.xlsx") #Export max values of plate
write.xlsx(Mean, "../data/Plate2_Mean.xlsx") #Export Mean values of plate
write.xlsx(SD, "../data/Plate2_SD.xlsx") #Export StDev values of plate
write.xlsx(CV, "../data/Plate2_CV.xlsx") #Export CV values of plate
write.xlsx(TMResults, "../data/Plate2_TMResults.xlsx") #Export TMResults values of plate

```
