---
title: "Week 6"
author: "Rachael Valdez"
date: "9/27/2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

## R Functions


*functions made w/ fucntion function

```{r functionExample}
myFunction <- function(x){
  print(x)
}
```

The above code creates a new function `myfunction`. It takes a single argument `x`, and when the fucntion executes, it will print content of `x ` to console (or output documnet)

```{r functionEx2}
myFunction(x = 2)

myFunction(x = c(1,2,3,4))
```

This basic fucntion is fairly useless, since it recreaes the existing `print()` function. Normally you owuld insert more code in curly braces to do  operations



```{r fucntionEx3}
myFunction2 <- function(x, y) {
  z = x + y
  z
}

result = myFunction2(2,4)
print(result)
```

Note that in code above, we run fuction and assign results to new variable callded `result`. If we run function w/o assigning it a results to a varialbe it owuld just print out.
The ocntents of `z` to the console

```{r SEfunction}
mySE <- function(x){
  #assume the input x is a vector of numbers
  #First calculate variance
  myvar = var(x)
  #then calc number of values in the samples
  myn = length(x)
  #bext cakc tge sq riit if varuabcem duvude bt sanoke suze
  mySE = sqrt( myvar/myn)
  #the value returned will be last object created in the function, in this case mySE
  mySE #repeating just the last variable here will cause the result to print out when run
}
```

Now we can test the funciton
```{r testSE}
x = c(1,1,3,3,6,6)
mySE(x) #result should be 0.9189366
```

*There are functions in R that will only take the name of another function as an argument. ex aggregate function.

```{r aggregateCustomFunction}
#make a practice data frame
mydf = data.frame(Group = c(rep('A', 6), rep('B', 6)),
                  Values = c(1,2,3,4,5,6,11,22,33,44,55,66))
mydf #print it out
#calc standard error of group A (row 1-6)
mySE(mydf$Values[1:6])
#calc SE of group B (rows1-6)
mySE(mydf$Values[1:6])

#now our custom mySE function inside aggregate to accomplish same thing
aggregate(Values~Group, data = mydf, FUN = mySE)
```




