---
title: "HW3"
author: "Rachael Valdez"
date: "9/19/2017"
output: 
  word_document:
    fig_caption: yes
  pdf_document: default
  html_document:
    fig_caption: yes
---
## R Markdown File
This file will contain an analysis of the salary distribution between the different levels of accounting technicians in the CSU system for 2015. 

## R setup
Will use function 'knitr' so we can use function 'kable' later on.
Function 'fig.align' is used to center figures.

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

## Set Working Directory
The working directory will set the current file path. In a .Rmd file, the directory paths to data files will need to be set relative to the sotrage of the .Rmd file, so a working directory will not be necessary. An example of how one would normally set a working directory is below. 
```{r workingdir}
# setwd("~/Desktop/Files/Biol255E/")
```

## Data Import
We begin by importing the data from the california-state-university-2015.csv file. 

```{r data import}
df = read.csv("../data/california-state-university-2015.csv")
```

## Data subsetting
I will subset the data for accounting technician I, II and III.

```{r data segregation by job title}
ATI = df[df$Job.Title == 'ACCOUNTING TECHNICIAN I',]
ATII = df[df$Job.Title == 'ACCOUNTING TECHNICIAN II',]
ATIII = df[df$Job.Title == 'ACCOUNTING TECHNICIAN III',]
```

## Merging data for accounting technician I, II and III
Data for accounting technician I, II and III were separated into 3 data sets. All three will be merged using the function 'rbind'.

```{r bind}
ATS = rbind(ATI, ATII, ATIII)
```

## Factors
Function 'factor' is used to order factors of the categorical data.
```{r factor}
ATS$Job.Title = factor(ATS$Job.Title)
```

## Plot
Now we will make a boxplot for accounting technicians I, II and III showing the distribution of saleries in each job category. 

```{r boxplot}
boxplot(ATS$Base.Pay~ATS$Job.Title, 
        names = c("ATI", "ATII", "ATIII"),
        main = "Salary Distribution of Accounting Technician\'s",
        ylab = 'Thousands',
        xlab = 'Accounting Technician(AT)',
        col = c('lavender', 'violet', 'purple'))
```

## Results
Print out R results of mean calculation to output.

```{r mean calculation}
mymean=(aggregate(ATS$Base.Pay~ATS$Job.Title, 
                data = ATS, FUN = mean))
#mymean prints output
```

## Mean Table
Will layout means in a table, showing mean for each accounting technician level. 
```{r mean Table, results='asis'}
kable(mymean, caption = 'Mean pay per AT') 
```